Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-09 Grassmannian_cells.tex
Minor edits in Section 2 and Prop. 3.3

For an introduction to covering theory we refer to \cite{gab}.
Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:s(\alpha)\to t(\alpha)$.
A $\CC$-representation $X$ of $Q$ consists of a collection of $\CC$-vector spaces $X_i$ for $i\in Q_0$ and a collection of $\CC$-linear maps $X_\alpha:X_{s(\alpha)}\to X_{t(\alpha)}$ for $\alpha\in Q_1$.
Given $\CC$-representations $X$ and $Y$ of $Q$, a morphism $f:X\to Y$ is a collection of $\CC$-linear maps $f_i:X_i\to Y_i$ for $i\in Q_0$ satisfying $f_{t(\alpha)}\circ X_\alpha=Y_\alpha\circ f_{s(\alpha)}$ for each $\alpha\in Q_1$.
Write $\Rep(Q)$ for the abelian category of $\C$-representations of $Q$.

@@

Let $W_Q$ be the free non-abelian group generated by $Q_1$.  
Write $A_Q\cong \ZZ^{Q_1}$ for the free abelian group generated by $Q_1$ and denote by $e_\alpha\in A_Q$ the generator corresponding to $\alpha\in Q_1$. 
\begin{definition}
  The \emph{universal abelian covering quiver} $\hat Q$ of $Q$ has vertices $\hat Q_0=Q_0\times A_Q$ and arrows $\hat Q_1=Q_1\times A_Q$, where $(\alpha,\chi):\big(s(\alpha),\chi\big)\to\big(t(\alpha),\chi+e_\alpha\big)$ for $\alpha\in Q_1$ and $\chi\in A_Q$.
  Write $F_Q:\Rep(\hat Q)\to\Rep(Q)$ for the natural functor.

  The \emph{universal covering quiver} $\widetilde Q$ of $Q$ has vertices $\widetilde Q_0=Q_0\times W_Q$ and arrows $\widetilde Q_1=Q_1\times W_Q$, where $(\alpha,w):\big(s(\alpha),w\big)\to\big(t(\alpha),w\alpha\big)$ for $\alpha\in Q_1$ and $w\in W_Q$.
  Write $G_Q:\Rep(\widetilde Q)\to\Rep(Q)$ for the natural functor.

  We say that a representation $X\in\Rep(Q)$ can be \emph{lifted} to $\hat Q$ (resp. $\widetilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp. $\widetilde X\in\Rep(\widetilde Q)$) such that $F_Q\hat X=X$ (resp. $G_Q \widetilde X=X$).
\end{definition}

Note that in our definition every covering quiver has infinitely many connected components, but each of its connected components is a covering in the sense of \cite{gab}.
As indecomposable representations live on one of these components this distinction will be irrelevant.
Note that the natural surjection $W_Q\onto A_Q$ induces a functor $H_Q:\Rep(\widetilde Q)\to\Rep(\hat Q)$.
In addition, observe that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.

\begin{lemma}
  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and $\widetilde Q$.
\end{lemma}
\begin{proof}
  This statement is clear for the simple representations $S_i$, $i\in Q_0$.
  Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
  Applying a BGP-reflection to a vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)$ of $\hat Q$ (resp. $(i,w)$ of $\widetilde Q$).
  This gives the claim.
\end{proof}

The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
We say that a dimension vector $\hat \bfe$ of $\hat Q$ is \emph{compatible} with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
The group $A_Q$ acts on $\hat Q$ via translation, this induces actions of $A_Q$ on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
We say two representation (resp. dimension vectors) are \emph{equivalent} if they can be related by the action of $A_Q$.
The analogous observation can also be made for $\widetilde Q$.
If $M$ is a representation of $\hat Q$ (resp. $\widetilde Q$), we denote by $M_\chi$ (resp. $M_w$) the representation obtained via translation by $\chi\in A_Q$ (resp. $w\in W_Q$).

As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain the following result from \cite{gab}.
\sayD{Citation needed?}
\begin{theorem}
  \label{covering}
  The functors $F_Q$ and $G_Q$ preserve indecomposability.
  Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
  \[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\hat Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\hat Q}(\hat X,\hat Y_\chi).\]
  Analogous isomorphisms exist when replacing $\Hom$ by $\Ext$ or $\Rep(\hat Q)$ by $\Rep(\widetilde Q)$.
\end{theorem}

@@

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  \label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are short exact sequences without any preinjective direct summands.
      %Without the assumption on the direct summands, it is not clear that short exact sequences are preserved.
      %This is because $\Sigma_2 S_2=0$.
  \end{enumerate}
\end{remark}
We will see that the indecomposable representations of dimension $\alpha(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
For a dimension vector $\alpha$, write $R_\alpha(K(n))$ for the affine space of representations of dimension $\alpha$.
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  %\sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of dimension $\alpha(m,r)$ are in one-to-one correspondence to points of $\Gr_{n-r}(\CC^n)$.
    \item The set of indecomposable representations of dimension $\alpha(m,r)$ is given by a non-empty open subset of $R_{\alpha(m,r)}(K(n))$. 
   % \item The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and as we have $\Sigma_2(\alpha(m,r))=\alpha(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $\alpha(m,r)=(1,d)$ for $d:=n-r$.
  This means that $X\in R_\alpha(K(n))$ is given by a matrix $M_X\in\CC^{d\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=d$.
  Indeed, $X$ admits a summand isomorphic to $S_1^m$ exactly when $\rk(M_X)=d-m$.

  This shows that the indecomposable representations in $R_{\alpha(1,d)}(K(n))$ are in one-to-one correspondence with $d\times n$ matrices of maximal rank.
  Thus they are in one-to-one correspondence to subspaces of $\CC^n$ of dimension $d$ spanned by the column vectors of $M_X$.
  Now it is straightforward to check that the $\Gl_\alpha=\CC^\ast\times\Gl_d(\CC)$-action on $R_\alpha(K(n))$ corresponds to the base change action of $\Gl_d(\CC)$ on the set of subspaces.
  This shows the first statement.

  It can be checked straightforwardly that $\alpha(1,d)$ is a Schur root because all indecomposable representations have trivial endomorphism ring.
  Thus the roots $\alpha(m,d)$ are also Schur roots.
  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{\alpha(m,r)}(K(n))$, see for example \cite{sch}.
  This shows the second statement.

%For $m=1$, the action of $\Gl_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_\alpha(K(n))$. As the reflection functors preserve indecomposability and isomorphism classes, by Lemma \ref{compatibleGSigma}, for every $g\in\Gl_n(\CC)$, we obtain a commutative diagram
%\[\xymatrix{\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}\ar[d]^{g^{-T}}&\Ind(K(n),\alpha(m+1,r))\ar[d]^g\\
%\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}&\Ind(K(n),\alpha(m+1,r))}\]
%As the $\Gl_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
\end{proof}
\begin{remark}
  There is a more elegant way to prove Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
  Actually, fixing the standard stability induced by the linear form $\Theta(\alpha)=\alpha_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representation is in fact $\Gr_d(\CC^n)$.
  We opted for the proof above because the notion of stability would only be used at this point and we wanted to keep the exposition as simple as possible. 
\end{remark}

@@

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
  Moreover, $\Hom(P_{m+1},P_{m+1}^V)$ is the one-dimensional space spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{lemma}
\begin{proof}
  The first claim is immediate since $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.\sayT{this is maybe not clear as we do not know that $P_{m+1}^V$ is indecomposable?! Therefore, I added a sentence.} Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0.$  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{proof}

@@

\begin{remark}
  \mbox{}
  \begin{enumerate}
    \item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_Q$ on $\Rep(\widetilde{K(n)})$. 
      %Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
    \item We have 
      $$\tilde P_{2l-1,i}:=\alpha_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=\alpha_i^{-1}.\tilde P_{2l}$$
      for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).

@@

Let $Q$ be an acyclic quiver. We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\Rep(Q)$ which can be lifted to $\hat Q$. We can consider the decomposition $X_q=\bigoplus_{(q,\chi)\in A_Q} X_{(q,\chi)}$. We define a torus action on each $X_{(q,\chi)}$ via $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ which can be extended linearly to each $X_q$. For a fixed a subspace $U_q$, we can define the subspace $t.U_q$. In general, this torus action induces no torus action on the Quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$. Actually, such an action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$. 
\begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
If $X\in\Rep(Q)$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $\chi\in A_{Q}$.
\end{lemma}
\begin{proof} 
  Let $U\in \Gr_\bfe(X)$. Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$. Let $u_{(i,\chi)}\in U_{(i,\chi)}$ and $\alpha:i\to j\in Q_1$. Then we have $X_\alpha(u_{(i,\chi)})\in U_{(j,\chi+e_\alpha)}$ because $X$ can be lifted to the universal cover. Then it follows
\[X_\alpha(t.u_{(i,\chi)})=X_\alpha(t^{d(i,\chi)}u_{(i,\chi)})=t^{d(i,\chi)}X_\alpha(u_{(i,\chi)})=t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}t.u_{(j,\chi+e_\alpha)}\]
for some $u_{(j,\chi+e_\alpha)}\in U_{(j,\chi+e_\alpha)}$.
Now we have \[\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{c(j,\chi)}t.U_{(j,\chi)}\]
for every $t\in\C^\ast$ if $c(j,\chi)$ is constant along $(j,\chi)\in \{j\}\times A_Q$. This yields  
\[t.U_j=\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{-c_\alpha}t.U_{(j,\chi)}\]
for every $t\in \C^\ast$.
\end{proof}

>>>>

For an introduction to covering theory we refer to \cite{gab}.
Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:s(\alpha)\to t(\alpha)$.
A $\CC$-representation $X$ of $Q$ consists of a collection of $\CC$-vector spaces $X_i$ for $i\in Q_0$ and a collection of $\CC$-linear maps $X_\alpha:X_{s(\alpha)}\to X_{t(\alpha)}$ for $\alpha\in Q_1$.
Given $\CC$-representations $X$ and $Y$ of $Q$, a morphism $f:X\to Y$ is a collection of $\CC$-linear maps $f_i:X_i\to Y_i$ for $i\in Q_0$ satisfying $f_{t(\alpha)}\circ X_\alpha=Y_\alpha\circ f_{s(\alpha)}$ for each $\alpha\in Q_1$.
Write $\rep Q$ for the abelian category of $\C$-representations of $Q$.

@@

Let $W_Q$ be the free non-abelian group generated by $Q_1$.  
Write $A_Q\cong \ZZ^{Q_1}$ for the free abelian group generated by $Q_1$ and denote by $e_\alpha\in A_Q$ the generator corresponding to $\alpha\in Q_1$. 
\begin{definition}
  The \emph{universal abelian covering quiver} $\hat Q$ of $Q$ has vertices $\hat Q_0=Q_0\times A_Q$ and arrows $\hat Q_1=Q_1\times A_Q$, where $(\alpha,\chi):\big(s(\alpha),\chi\big)\to\big(t(\alpha),\chi+e_\alpha\big)$ for $\alpha\in Q_1$ and $\chi\in A_Q$.
  Write $F_Q:\rep \hat Q\to\rep Q$ for the natural functor.

  The \emph{universal covering quiver} $\widetilde Q$ of $Q$ has vertices $\widetilde Q_0=Q_0\times W_Q$ and arrows $\widetilde Q_1=Q_1\times W_Q$, where $(\alpha,w):\big(s(\alpha),w\big)\to\big(t(\alpha),w\alpha\big)$ for $\alpha\in Q_1$ and $w\in W_Q$.
  Write $G_Q:\rep\widetilde Q\to\rep Q$ for the natural functor.

  We say that a representation $X\in\rep Q$ can be \emph{lifted} to $\hat Q$ (resp. $\widetilde Q$) if there exists a representation $\hat X\in\rep \hat Q$ (resp. $\widetilde X\in\rep \widetilde Q$) such that $F_Q\hat X=X$ (resp. $G_Q \widetilde X=X$).
\end{definition}

Note that in our definition every covering quiver has infinitely many connected components, but each of its connected components is a covering in the sense of \cite{gab}.
As indecomposable representations live on one of these components this distinction will be irrelevant.
Note that the natural surjection $W_Q\onto A_Q$ induces a functor $H_Q:\rep \widetilde Q\to\rep \hat Q$.
In addition, observe that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.

\begin{lemma}
  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and $\widetilde Q$.
\end{lemma}
\begin{proof}
  This statement is clear for the simple representations $S_i$, $i\in Q_0$.
  Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
  Applying a BGP-reflection to a fixed vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)\in\hat Q_0$ where $\chi$ runs through all $\chi\in A_Q$ (resp. to all $(i,w)\in \tilde Q_0$ with $w\in W_Q$).
  This gives the claim.
\end{proof}

The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
We say that a dimension vector $\hat \bfe$ of $\hat Q$ is \emph{compatible} with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
The group $A_Q$ acts on $\hat Q$ via translation, this induces actions of $A_Q$ on $\rep\hat Q$ and on $\ZZ^{\hat Q_1}$.
We say two representation (resp. dimension vectors) are \emph{equivalent} if they can be related by the action of $A_Q$.
The analogous observation can also be made for $\widetilde Q$.
If $X$ is a representation of $\hat Q$ (resp. $\widetilde Q$), we denote by $X_\chi$ (resp. $X_w$) the representation obtained via translation by $\chi\in A_Q$ (resp. $w\in W_Q$).

As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain the following result from \cite{gab}.
\sayD{Citation needed?}
\begin{theorem}
  \label{covering}
  The functors $F_Q$ and $G_Q$ preserve indecomposability.
  Moreover, for all representations $\hat X,\hat Y \in\rep(\hat Q)$, we have 
  \[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\hat Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\hat Q}(\hat X,\hat Y_\chi).\]
  Analogous isomorphisms exist when replacing $\Hom$ by $\Ext$ and/or $\rep \hat Q$ by $\rep\widetilde Q$.
\end{theorem}

@@

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  \label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are short exact sequences without any preinjective direct summands.
      %Without the assumption on the direct summands, it is not clear that short exact sequences are preserved.
      %This is because $\Sigma_2 S_2=0$.
  \end{enumerate}
\end{remark}
We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
For a dimension vector $d\in\NN^{Q_0}$, write $R_d(K(n))$ for the affine space of representations of dimension $\alpha$.
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  %\sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of dimension $\alpha(m,r)$ are in one-to-one correspondence to points of $\Gr_{n-r}(\CC^n)$.
    \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
   % \item The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and as we have $\Sigma_2(d(m,r))=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $d(m,r)=(1,l)$ for $l:=n-r$.
  This means that $X\in R_{d(m,r)}(K(n))$ is given by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
  Indeed, $X$ admits a summand isomorphic to $S_1^m$ exactly when $\rk(M_X)\leq l-m$.

  This shows that the indecomposable representations in $R_{(1,l)}(K(n))$ are in one-to-one correspondence with $l\times n$ matrices of maximal rank.
  Thus they are in one-to-one correspondence to subspaces of $\CC^n$ of dimension $l$ spanned by the column vectors of $M_X$.
  Now it is straightforward to check that the $\Gl_\alpha=\CC^\ast\times\Gl_l(\CC)$-action on $R_{d(m,r)}(K(n))$ corresponds to the base change action of $\Gl_l(\CC)$ on the set of subspaces.
  This shows the first statement.

  It can be checked straightforwardly that $(1,l)$ is a Schur root because all indecomposable representations have trivial endomorphism ring.
  Thus the roots $d(m,r)$ are also Schur roots.
  It follows that the set of indecomposable representations with trivial endomorphism ring form a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite{sch}.
  This shows the second statement.

%For $m=1$, the action of $\Gl_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_\alpha(K(n))$. As the reflection functors preserve indecomposability and isomorphism classes, by Lemma \ref{compatibleGSigma}, for every $g\in\Gl_n(\CC)$, we obtain a commutative diagram
%\[\xymatrix{\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}\ar[d]^{g^{-T}}&\Ind(K(n),\alpha(m+1,r))\ar[d]^g\\
%\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}&\Ind(K(n),\alpha(m+1,r))}\]
%As the $\Gl_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
\end{proof}
\begin{remark}
  There is a more elegant way to prove Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces.
  Actually, fixing the standard stability induced by the linear form $\Theta(\alpha)=\alpha_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_l(\CC^n)$.
  We opted for the proof above because the notion of stability would only be used at this point and we wanted to keep the exposition as simple as possible. 
\end{remark}

@@

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
  Moreover, $\Hom(P_{m+1},P_{m+1}^V)$ is the one-dimensional space spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{lemma}
\begin{proof}
  The first claim is immediate since $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.\sayT{The proof as written seems to be false as $\Hom(X,P_\ell)\ne0$ does not imply $\Hom(Y,P_\ell)\neq 0$ for all direct summands $Y$ of $X$. } Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0.$  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{proof}

@@

\begin{remark}
  \mbox{}
  \begin{enumerate}
    \item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_Q$ on $\rep\widetilde{K(n)}$. 
      %Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
    \item We have 
      $$\tilde P_{2l-1,i}:=\alpha_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=\alpha_i^{-1}.\tilde P_{2l}$$
      for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).

@@

Let $Q$ be an acyclic quiver. We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\rep Q$ which can be lifted to $\hat Q$. We can consider the decomposition $X_q=\bigoplus_{(q,\chi)\in A_Q} X_{(q,\chi)}$. We define a torus action on each $X_{(q,\chi)}$ via $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ which can be extended linearly to each $X_q$. For a fixed a subspace $U_q$, we can define the subspace $t.U_q$. In general, this torus action induces no torus action on the Quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$. Actually, such an action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$. 
\begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
If $X\in\rep Q$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $\chi\in A_{Q}$.
\end{lemma}
\begin{proof} 
  Let $U\in \Gr_\bfe(X)$. Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$. Let $u_{(i,\chi)}\in U_{(i,\chi)}$ and $\alpha:i\to j\in Q_1$. Then we have $X_\alpha(u_{(i,\chi)})\in U_{(j,\chi+e_\alpha)}$ because $X$ can be lifted to the universal cover. Then it follows
\[X_\alpha(t.u_{(i,\chi)})=X_\alpha(t^{d(i,\chi)}u_{(i,\chi)})=t^{d(i,\chi)}X_\alpha(u_{(i,\chi)})=t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}t.u_{(j,\chi+e_\alpha)}\]
for some $u_{(j,\chi+e_\alpha)}\in U_{(j,\chi+e_\alpha)}$.
Now we have \[\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{c(j,\chi)}t.U_{(j,\chi)}\]
for every $t\in\C^\ast$ if $c(j,\chi)$ is constant along $(j,\chi)\in \{j\}\times A_Q$. This yields  
\[t.U_j=\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{-c_\alpha}t.U_{(j,\chi)}\]
for every $t\in \C^\ast$.
\end{proof}
